---
title: "R FUNDAMENTALS - IP WEEK 12"
output: html_document
---
# Defining the Question
We will work as data scientists for a Kenyan entrepreneur who runs an online cytography course and would like for us to help her identify which individuals are most likely to click on her ads.

# Metric for Success

We will perform bivariate and univariate analysis and successfully identify the individuals that are most likely to click on the ads

# Experimental Design
1.Defining the Question
2.Data Cleaning
3.Exploratory Data Analysis
4.Conlusion and Recommendation
5.Challenging the Solution

# Data Preparation
Reading the Data

```{r}
#Setting up the environment
getwd()
#locating the dataset
setwd("C:/Users/user/Documents/advertising")

#Checking for the particular file
list.files()
#loading the dataset
df <- read.table("advertising.csv", sep = ",", header = TRUE)
```

```{r}
#Checking the size of the dataset
file.info("C:/Users/user/Documents/advertising/advertising.csv")$size
#taking a look at the dataset, there are 339 rows and 10 columns
str(df, 5)
#Checking for structural errors
#Seemingly there are no mislabeled columns
```

```{r}
unique(df)
```

```{r}
summary(df)
```

```{r}
#To use the describe function so as to get summary statistics we will install psych package first 
install.packages("psych")
```

```{r}
library(psych)
```

```{r}
describe(df)
```

```{r}
#Checking for outliers. This shows no outliers in the aga and Day time spent online
for (i in 1:2) {
  boxplot(df[,i], main=names(df)[i], horizontal = TRUE)}
```

```{r}
#There just one outlier in the Area Income column and we'll keep it. 
outlier_values <- boxplot.stats(df$Area.Income)$out  # outlier values.
boxplot(df$Area.Income, main="Area Income Outliers", boxwex=0.1)
mtext(paste("Outliers: ", paste(outlier_values, collapse=", ")), cex=0.6)
```
# Exploratory Data Analysis
Univariate Analysis
```{r}
install.packages("magrittr")
```

```{r}
install.packages("dplyr")
```

```{r}
library(magrittr)
library(dplyr)
```

```{r}
install.packages("DataExplorer")
```

```{r}
library(DataExplorer)
```

```{r}
plot_intro(df)
```

```{r}
install.packages("ggplot2")
```

```{r}
library(ggplot2)
```

```{r}
ggplot(data = df) +
  geom_bar(mapping = aes(x = Age))
```


```{r}
DataExplorer::plot_histogram(df$Daily.Internet.Usage)
```

Bivariate Analysis
```{r}

cor(df$Age,df$Clicked.on.Ad, method = c("pearson", "kendall", "spearman"))

```
Moderate positive relationship: Some points are close to the line but other points are far from it, which indicates only a moderate linear relationship between the variables.

```{r}
cor(df$Daily.Internet.Usage,df$Clicked.on.Ad, method = c("pearson", "kendall", "spearman"))
```
Large negative relationship: The points fall close to the line, which indicates that there is a strong negative relationship between the variables. The relationship is negative because, as one variable increases, the other variable decreases.

```{r}
cor(df$Clicked.on.Ad,df$Daily.Internet.Usage, method = c("pearson", "kendall", "spearman"))

```


Large negative relationship: The points fall close to the line, which indicates that there is a strong negative relationship between the variables. The relationship is negative because, as one variable increases, the other variable decreases.

```{r}
cor(df$Clicked.on.Ad,df$Male, method = c("pearson", "kendall", "spearman"))
```

No relationship:The points fall randomly on the plot, which indicates that there is no linear relationship between the variables.

```{r}
install.packages("ggplot2")
library(ggplot2)

```

```{r}
ggplot(df, aes(x = Age, y = Area.Income)) + geom_point()
```

```{r}
ggplot(df, 
       aes(x = Male, 
           y = Clicked.on.Ad)) +
  geom_bar(stat = "identity")
```
```{r}
ggplot(df, 
       aes(x = Age, 
           y = Clicked.on.Ad)) +
  geom_bar(stat = "identity", fill = "cornflowerblue")
```

# Conclusion and Recommendation
The age of an individual was the top feature in determining clicking on an advert followed by Daily Internet Usage of which the maximum time spent online was 267minutes. 45years is the age that Clicked on the adverts the most, followed by 31 year individuals. Female individuals clicked on ads more than men. 

# Challenging the Solution
I was unable to do research on Cities and Countries that clicked on ads and this needs to be investigated further. 





